Hippocampal replay of experience at slow speeds

### 2021-05-05 Article.tex

\subsection*{Software and Code Availability}
Python code used for analysis and generating figures in the paper is available at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_paper}. Code for the classifier is available in a separate software repository to facilitate code reuse at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_classification} (doi: 10.5281/zenodo.3713412).
Both code bases rely on the following python packages: Numpy \citep{vanderWaltNumPyArrayStructure2011}, Numba \citep{LamNumbaLLVMbasedPython2015}, Matplotlib \citep{HunterMatplotlib2DGraphics2007}, xarray \citep{HoyerxarrayNDlabeled2017}, NetworkX \citep{HagbergExploringNetworkStructure2008}, Pandas \citep{McKinneyDataStructuresStatistical2010} and Seaborn \citep{Waskomseabornstatisticaldata2021}. All code is open-source and licensed under the MIT Software License. Classifier code can be easily installed as a python package with all requisite dependencies using pip or conda. See software repositories for specific details.

>>>>

\subsection*{Software and Code Availability}
Python code used for analysis and generating figures in the paper is available at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_paper}. Code for the classifier is available in a separate software repository to facilitate code reuse at: \url{https://github.com/Eden-Kramer-Lab/replay_trajectory_classification} (doi: 10.5281/zenodo.3713412).
Both code bases rely on the following python packages: Numpy \citep{vanderWaltNumPyArrayStructure2011}, Numba \citep{LamNumbaLLVMbasedPython2015}, Matplotlib \citep{HunterMatplotlib2DGraphics2007}, xarray \citep{HoyerxarrayNDlabeled2017}, NetworkX \citep{HagbergExploringNetworkStructure2008}, Pandas \citep{McKinneyDataStructuresStatistical2010} and Seaborn (doi: 10.5281/zenodo.883859). All code is open-source and licensed under the MIT Software License. Classifier code can be easily installed as a python package with all requisite dependencies using pip or conda. See software repositories for specific details.
